Mean and variance functions used to simulate Gaussian data

### 2018-12-04 analysis/gaussian_signals.Rmd
wflow_publish("gaussian_signals.Rmd")

```{r plot-variance-functions}
plot(t,var1,xlab = "",ylab = "",ylim = c(0,1),type = "l",
     main = "Constant variance function")
plot(t,var2,xlab = "",ylab = "",type = "l",
     main = "Triple exponential variance function")
plot(t,var3,xlab = "",ylab = "",type = "l",main = "Doppler variance function")
plot(t,var4,xlab = "",ylab = "",type = "l",main = "Bumps variance function")
plot(t,var5,xlab = "",ylab = "",type = "l",main = "Clipped variance function")
```

>>>>

```{r plot-variance-functions, fig.height=7.5, fig.width=6}
plot_grid(
  qplot(t,var1,geom="line",xlab="",ylab="",main="Constant variance (v1)"),
  qplot(t,var2,geom="line",xlab="",ylab="",main="Triple exponential (v2)"),
  qplot(t,var3,geom="line",xlab="",ylab="",main="Doppler (v3)"),
  qplot(t,var4,geom="line",xlab="",ylab="",main="Bumps (v4)"),
  qplot(t,var5,geom="line",xlab="",ylab="",main="Clipped (v5)"),
  nrow = 3,ncol = 2)
```
